Relating two Abstractions for Formal Array Languages

### 2014-04-11 paper.tex
looks good
I made one typo change and added a footnote about materialization. Let
me know what else we should do.

Fusion is a powerful optimization which allows programming on a high
level by composing functions without paying an performance penalty.

Fusion effectively makes Pull arrays \emph{virtual} in that they will
not be represented in memory. All intermediate arrays will be
removed. But sometimes it is important to keep an array in memory, not
least to produce the final result. For this reason, Pull arrays
provide a function, variously known as \verb!force!, \verb!memorize!
  or \verb!store!. We will refer to it as \verb!store! here. The
  functional semantics of \verb!store! is the identity function,
  i.e. it simply returns the same array as it was given. However, as a
  side effect it stores the array to memory.

>>>>

Fusion is a powerful optimization which allows programming on a high
level by composing functions without paying a performance penalty.

Fusion effectively makes Pull arrays \emph{virtual} in that they will
not be represented in memory. All intermediate arrays will be
removed. But sometimes it is important to keep an array in memory
\footnote{Example: Indexing a huge transposed array that has a few rows and many columns. Non-materialization
may cause many cache misses and page faults.}, 
not least to produce the final result. For this reason, Pull arrays
provide a function, variously known as \verb!force!, \verb!memorize!
  or \verb!store!. We will refer to it as \verb!store! here. The
  functional semantics of \verb!store! is the identity function,
  i.e. it simply returns the same array as it was given. However, as a
  side effect it stores the array to memory.
